An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex

  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
  For any $p\in\simplex$, we have
  \begin{align*}
    \risk{L}(p)
    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}
    \\
    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
    \\
    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
    \\
    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
  \end{align*}
  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
\end{proof}

@@

In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by
%\begin{align}\label{eq:abstain-discrete}
$\ellabs{\alpha}(r)_y = \begin{cases}
0 & r = y\\
\alpha & r = \bot\\
1 & \text{otherwise}
\end{cases}~.$
%\end{align}
Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max_{j \in [d]}B(y)_j u_j + 1\right)_+~,
\end{equation}
where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

>>>>

  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
  For any $p\in\simplex$, we have
  \begin{align*}
    \risk{L}(p)
    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}
    = -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)
    = -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
  \end{align*}
  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
\end{proof}

@@

In classification settings with a large number of labels, several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option.
For example, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r) = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
Here, the report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citet{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$ their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
\end{equation}
where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
